Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-22 Draft/contributions.tex
fix a bunch of typos

At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the QCD background $\mathcal{O}(\alphas^2\alpha^4)$ and the interference $\mathcal{O}(\alphas\alpha^5)$.\\
The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO. EW contribution in red, QCD in green, interference in gray and sum in blue. No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied. Results of full LO matrix element simulation.}
\label{fig:mjjdyjj_1d}
\end{figure*}
Concerning the QCD contribution, it is worth noticing that for quantum number conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed. The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions). The LO cross--section for the three perturbative orders are shown in table~\ref{tab:LOscanXsec}.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas^2\alpha^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas\alpha^5))$ \\
        \hline
        \hline
        {\sc Phantom}  &  $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
        {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process: these results concern the setup described in section~\ref{subsec:inputpar}, apart from the $M_{jj}$ and $|\Delta y_{jj}|$ cuts which have been dropped.}
\end{table}
The EW, QCD and interference amount respectively to 57\%, 37\% and 6\% of the total inclusive cross section. In the presence of typical VBS cuts, the EW contribution is strongly enhanced, as shown in section~\ref{subsec:LOfiducial}.\\
The EW contribution to the $M_{jj}$ distribution (red curve in Fig.~\ref{fig:mjjdyjj_1d}) shows a huge peak around the $W$ mass: this is due to the possibility for the two jets to be decay products of a $W^-$ boson. Note that this effect doesn't arise in calculations which employ VBS approximation (see VBS approx. description in section [ref.]).
One can also see this in three different plots in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alpha^5\alphas)$ (top right), and $\mathcal{O}(\alpha^4 \alphas^2)$ (bottom).}
\label{fig:mjjdyjj_2d_LO}
\end{figure}

>>>>

At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$ and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.\\
The three contributions to the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO. EW contribution in red, QCD in green, interference in gray and sum in blue. No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied. Results of full LO matrix element simulation.}
\label{fig:mjjdyjj_1d}
\end{figure*}
Concerning the QCD contribution, it is worth noticing that for quantum number conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed. The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions). The LO cross--section for the three perturbative orders are shown in table~\ref{tab:LOscanXsec}.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas^2\alpha^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas\alpha^5))$ \\
        \hline
        \hline
        {\sc Phantom}  &  $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
        {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process: these results concern the setup described in section~\ref{subsec:inputpar}, apart from the $M_{jj}$ and $|\Delta y_{jj}|$ cuts which have been dropped.}
\end{table}
The EW, QCD and interference amount respectively to 57\%, 37\% and 6\% of the total inclusive cross section. In the presence of typical VBS cuts, the EW contribution is strongly enhanced, as shown in section~\ref{subsec:LOfiducial}.\\
The EW contribution to the $M_{jj}$ distribution (red curve in Fig.~\ref{fig:mjjdyjj_1d}) shows a huge peak around the $W$ mass: this is due to the possibility for the two jets to be decay products of a $W^-$ boson. Note that this effect doesn't arise in calculations which employ VBS approximation (see VBS approx. description in section [ref.]).
One can also see this in three different plots in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alpha^5\alphas)$ (top right), and $\mathcal{O}(\alpha^4 \alphas^2)$ (bottom).}
\label{fig:mjjdyjj_2d_LO}
\end{figure}

### 2018-01-22 Draft/definition.tex
Add a motivation and extend the introduction
- added a motivation (first paragraph)
- extended or added some explanations
- changed the process to include the `+ X`, since we are inclusive;
  TODO: make sure this is also used in the remaining document
- changes `section` and `Section` to `Sec.` if they are not at the
  beginning of a sentence (in `macros.tex` there are abbreviations for
  it so I assume that is the "correct" style)
- corrected some spelling mistakes
fix a bunch of typos

The scattering of two positively charge W bosons is proceeding at the LHC through the partonic process:
%
\begin{equation}
 {\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}.
\end{equation}

This process possesses three LO contributions of different orders.
The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ is referred to as EW contributions.
In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
These type of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO})
The VBS diagrams typically dominate the full process.
But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.

@@

Finally, due to the specific colour structure of these two classes of amplitudes, there exists non-zero interferences.
These are of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$ and are usually small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.

Usually, in experimental measurements, special VBS-cuts are designed in order to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have rather different kinematic.
The EW contribution is characterised by two jets with large rapidity in the peripheral region as well as a large invariant mass.
The two W bosons are mostly produced centrally.
This is in opposition with the QCD component which favour jets in the central region.
Therefore, the event selection usually involve rapidity-difference and invariance mass cuts for the jets.
This will also be discussed in Section \ref{subsec:contributions}.

>>>>

The scattering of two positively charged W bosons is proceeding at the LHC through the partonic process:
%
\begin{equation}
\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}.
\end{equation}

This process possesses three LO contributions of different orders.
The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ is referred to as EW contributions.
In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
These types of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
The VBS diagrams typically dominate the full process.
But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.

@@

Finally, due to the specific colour structure of these two classes of amplitudes, there exist non-zero interferences.
These are of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$ and are usually small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.

Usually, in experimental measurements, special VBS-cuts are designed in order to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have rather different kinematic.
The EW contribution is characterised by two jets with large rapidity in the peripheral region as well as a large invariant mass.
The two W bosons are mostly produced centrally.
This is in opposition with the QCD component which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariance mass cuts for the jets.
This will also be discussed in Section \ref{subsec:contributions}.

### 2018-01-22 Draft/description.tex
fix a bunch of typos

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computationsof one-loop amplitudes are carried out by switching dynamically between 
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which 
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections 
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections, 
        only loops with QCD-interacting particles are generated.
        \MP{Detail of the approximation done, divergent part, assumed to cancel etc.}

@@

  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
\MP{Mention the non-clustering for the scale as well as the different running of alphas at NLO.}

>>>>

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated.
        \MP{Detail of the approximation done, divergent part, assumed to cancel etc.}

@@

  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for matching NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
\MP{Mention the non-clustering for the scale as well as the different running of alphas at NLO.}

### 2018-01-22 Draft/input.tex
fix a bunch of typos

We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
density~\cite{Ball:2014uwa}
with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alphas\left( \MZ \right) = 0.118$. Since
the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
scheme, consistently with what is done in NNPDF.\\
We use the following values for the mass and width of the massive particles:
% 
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}. \\
\end{equation}
We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\

@@

Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}: 
\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
        is required to be
        \begin{align}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quark and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
        \begin{align}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
%         Finally, all jest in the event are required to be separated from charged leptons:
%         \begin{align}
%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
%         \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with 
        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
\end{itemize}

>>>>

We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton
density~\cite{Ball:2014uwa}
with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alphas\left( \MZ \right) = 0.118$. Since
the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularities are factorised with the  ${\overline{\rm MS}}$
scheme, consistently with what is done in NNPDF.\\
We use the following values for the mass and width of the massive particles:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}. \\
\end{equation}
We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\

@@

Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}:
\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
        is required to be
        \begin{align}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
        \begin{align}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
%         Finally, all jest in the event are required to be separated from charged leptons:
%         \begin{align}
%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
%         \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
\end{itemize}

### 2018-01-22 Draft/introduction.tex
fix a bunch of typos

Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs and can be longitudinally polarized.
The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge- and unitarity cancellations that strongly depend on the actual form of the Higgs-sector.
A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-standard model Higgs bosons.

The process with two positively charged W boson is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.

@@

At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest one are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on; in this article we will refer to it as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in later.
To our knowledge, such a detailed study was still missing.

>>>>

Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs and can be longitudinally polarized.
The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge- and unitarity cancellations that strongly depend on the actual form of the Higgs-sector.
A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-Standard Model Higgs bosons.

The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.

@@

At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest one are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on; in this article we will refer to it as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more detail later.
To our knowledge, such a detailed study was still missing.

### 2018-01-22 Draft/process.tex
fix a bunch of typos

A more refined approximation consists in considering all $t$- and $u$- diagrams and square them separately.
Nonetheless, different type of diagrams are not squared which amounts to neglecting interferences.
These interferences are expected to be small in the VBS fiducial region.
The $s$-channel contributions can still be left out.
This approximation is often called $t$-/$u$- approximation or even VBS approximation.
We will adopt the latter denomination in the following of the article.
Such an approximation is implemented at LO in the computer codes {\sc Bonsay} and {\sc Powheg}.
The physical origin of this approximation is that each proton emitting a quark represent two independent copies of $SU_c\left(3\right)$ gauge group.

@@

Moving on to NLO accuracy, one can extend the approximation presented at LO.
The VBS approximation at NLO is simply extending the same approximation to real as well as to virtual corrections.
This is implemented in {\sc POWHEG}.
This approximation can be used in combination with a double-pole approximation [REF] for the virtual contribution.
This require the computation of factorisable as well as non-factorisable corrections \cite{Dittmaier:2015bfe} separately.
Such an approximation is implemented in {\sc Bonsay}.
In {\sc VBFNLO}, the VBS approximation at NLO with $s$-channel contributions is implemented.

>>>>

A more refined approximation consists in considering all $t$- and $u$- diagrams and square them separately.
Nonetheless, different type of diagrams are not squared which amounts to neglecting interferences.
These interferences are expected to be small in the VBS fiducial region.
The $s$-channel contributions can still be left out.
This approximation is often called $t$-/$u$- approximation or even VBS approximation.
We will adopt the latter denomination in the following of the article.
Such an approximation is implemented at LO in the computer codes {\sc Bonsay} and {\sc Powheg}.
The physical origin of this approximation is that each proton emitting a quark represents two independent copies of the $SU_c\left(3\right)$ gauge group.

@@

Moving on to NLO accuracy, one can extend the approximation presented at LO.
The VBS approximation at NLO is simply extending the same approximation to real as well as to virtual corrections.
This is implemented in {\sc POWHEG}.
This approximation can be used in combination with a double-pole approximation [REF] for the virtual contribution.
This requires the computation of factorisable as well as non-factorisable corrections \cite{Dittmaier:2015bfe} separately.
Such an approximation is implemented in {\sc Bonsay}.
In {\sc VBFNLO}, the VBS approximation at NLO with $s$-channel contributions is implemented.
